A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-17 final project/Manuscript.Rmd
Moved Driven Growers to 3rd model

```{r}
#temp <- rbind(data.frame("Model" = c("1"), "Specificity" = model1_robust_results$specificity),
#              data.frame("Model" = c("2"), "Specificity" = model2_robust_results$specificity))%>%
temp <- rbind(data.frame("Model" = c("2"), "Specificity" = model2_robust_results$specificity))%>%
  mutate(Model = as.factor(Model))

ggplot(temp, aes(x = Specificity, fill = Model, color = Model)) +
  geom_density(alpha = 0.5) +
  ylab("Density") +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  #geom_vline(xintercept = mean(model1_robust_results$specificity), linetype="dashed", color = "#e41a1c") +
  geom_vline(xintercept = mean(model2_robust_results$specificity), linetype="dashed", color = "#377eb8")
```

@@

## Correlation Coefficients for Variables of Interest
```{r}
vars <- c("CARAVAN", "MOSTYPE", "PPERSAUT", "PBRAND", "MOSHOOFD", "APERSAUT", "LIKELY_CUSTOMERS")
temp <- up_train %>%
  mutate(CARAVAN = as.numeric(as.character(CARAVAN)),
         LIKELY_CUSTOMERS = as.numeric(as.character(LIKELY_CUSTOMERS)))
temp <- temp[vars]

@@

           "ABYSTAND", "LIKELY_CUSTOMERS"),

@@

                  "MOSTYPE = 12, 8, 6, 7, 1, 2, 36, 3, 37, 10, 20, 38, or 11"))

>>>>

```{r}
temp <- rbind(data.frame("Model" = c("1"), "Specificity" = model1_robust_results$specificity),
              data.frame("Model" = c("2"), "Specificity" = model2_robust_results$specificity))
temp <- 
  rbind(temp, data.frame("Model" = c("3"), "Specificity" = model3_robust_results$specificity))%>%
  mutate(Model = as.factor(Model))

ggplot(temp, aes(x = Specificity, fill = Model)) +
  geom_density(alpha = 0.5, color = NA) +
  ylab("Density") +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  geom_vline(xintercept = mean(model1_robust_results$specificity), linetype="dashed", color = "#e41a1c") +
  geom_vline(xintercept = mean(model2_robust_results$specificity), linetype="dashed", color = "#377eb8") +
  geom_vline(xintercept = mean(model3_robust_results$specificity), linetype="dashed", color = "#4daf4a") 
```

@@

## Correlation Coefficients for Variables of Interest
```{r}
vars <- c("CARAVAN", "MOSTYPE", "PPERSAUT", "PBRAND", "MOSHOOFD", "APERSAUT", "LIKELY_CUSTOMERS", "DRIVEN_GROWERS")
temp <- up_train %>%
  mutate(CARAVAN = as.numeric(as.character(CARAVAN)),
         LIKELY_CUSTOMERS = as.numeric(as.character(LIKELY_CUSTOMERS)))
temp <- temp[vars]

@@

           "ABYSTAND", "LIKELY_CUSTOMERS", "DRIVEN_GROWERS"),

@@

                  "MOSTYPE = 12, 8, 6, 7, 1, 2, 36, 3, 37, 10, 20, 38, or 11",
                  "MOSHOOFD = 2"))
